Data Preparation

### 2019-01-11 Data Preparation.Rmd
deletes space

# Save Data

```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview_stem, d_description_stem,
     file = "data_pillar_2.RDATA")
```

>>>>

# Save Data
```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview_stem, d_description_stem,
     file = "data_pillar_2.RDATA")
```
